---
title: "Agents Fundraising"
output: html_notebook
---

Examining trends in agent fund raising for miners. 

Using data pulled on Mar 26 2018 from Mining Intelligence

```{r}

library(tidyverse)

rawagents <- read_csv("C:/Users/Admin/Downloads/companies-capitalraisings-report-michael-mccrae-20180326135102-specialcharactersrem_delcol_remCRD.csv")
View(rawagents)


```




Next, separate the StartDate and ClosedDate into separate month, date and year

```{r}


rawagents_date <- rawagents %>% separate(col=StartDate,into=c(data="StartDateMonth", "StartDateDate", "StartDateYear"),sep=c("\\s","\\s"), remove="FALSE", convert="TRUE") %>% separate(col=ClosedDate,into=c(data="ClosedDateMonth", "ClosedDateDate", "ClosedDateYear"),sep=c("\\s","\\s"), remove="FALSE", convert="TRUE")

head(rawagents_date)



```



Let's select some of the useful columns


```{r}
usefulvar_rawagents <- rawagents_date %>% select(Agents, FinalAmountUSD, ClosedDateMonth, ClosedDateYear, Company)
head(usefulvar_rawagents)


```



Add a column from Agent that has three variables. I am using case_when: 

Brokered
Non-brokered
Not available

```{r}


library(stringr)
agents_b_nb_variable <- usefulvar_rawagents %>% mutate(brokered_nonbrokered=case_when(
  Agents=="Non-brokered" ~ "Non-brokered",
  Agents!= str_detect(Agents,"[a-z]") ~ "Brokered",
  TRUE ~ "Not Available"))
head(agents_b_nb_variable)


```


Do we have some oil sands in there? Let's get rid of since it skews the results.


```{r}

agents_three <- agents_b_nb_variable %>% filter(Company!="Cenovus Energy Inc.") 
agents_three

head(agents_three)



```


Set ClosedYearDate as a factor

```{r}

agents_three$ClosedDateYear <- as.factor(agents_three$ClosedDateYear)

str(agents_three)

```




Let's compare brokered, non-brokered totals 2016 vs. 2017


```{r}

agents_four<-agents_three %>% summarize(Sum_FinalAmountUSD=mean(FinalAmountUSD, na.rm=TRUE)) 


agents_four

?format()


```







Let's plot by year, brokered vs. nonbrokered.


```{r}

ggplot(agents_four, aes(x=ClosedDateYear, y=Sum_FinalAmountUSD, fill=brokered_nonbrokered)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=Sum_FinalAmountUSD))


```



