---
title: "Agents Fundraising"
output: html_notebook
---

Examining trends in agent fund raising for miners. 

Using data pulled on Mar 26 2018 from Mining Intelligence

```{r}
library(tidyverse)
rawagents <- read_csv("C:/Users/Admin/Downloads/companies-capitalraisings-report-michael-mccrae-20180326135102.csv")
rawagents
```


Next, separate the StartDate and ClosedDate into separate month, date and year

```{r}
rawagents_date <- rawagents %>% separate(col=StartDate,into=c(data="StartDateMonth", "StartDateDate", "StartDateYear"),sep=c("\\s","\\s"), remove="FALSE", convert="TRUE") %>% separate(col=ClosedDate,into=c(data="ClosedDateMonth", "ClosedDateDate", "ClosedDateYear"),sep=c("\\s","\\s"), remove="FALSE", convert="TRUE")

rawagents_date

```





Let's select some of the useful columns


```{r}
usefulvar_rawagents <- rawagents_date %>% select(Agents, FinalAmountUSD, ClosedDateMonth, ClosedDateYear, Company)
usefulvar_rawagents

```

Let's check all the companies in descending order. Do we have some oil sands in there? Let's get rid of since it skews the results.

```{r}

company_financing_total <- usefulvar_rawagents %>% filter(ClosedDateYear==2017) %>% group_by(Company) %>% summarise(n=sum(FinalAmountUSD)) %>% arrange(desc(n)) 
company_financing_total


```

 

Let's just look at 2017 and summarise Agents by total funds raised.

We will also filter out Cenovus. 



```{r}

agents_financings_total <- usefulvar_rawagents %>% filter(ClosedDateYear==2017) %>% filter(Company!="Cenovus Energy Inc.") %>% group_by(Agents) %>% summarise(n=sum(FinalAmountUSD)) %>% arrange(desc(n)) 
agents_financings_total

```


Add levels to ClosedDateMonth

```{r}

usefulvar_rawagents$ClosedDateMonth <-factor(usefulvar_rawagents$ClosedDateMonth, levels=c("Jan", "Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))

```




So what is the brokered vs. non-brokered monthly totals in 2017? 

```{r}

nonbrokered_monthly_totals <- usefulvar_rawagents %>% filter(ClosedDateYear==2017) %>% filter(Agents=="Non-brokered") %>% group_by(ClosedDateMonth) %>% summarise(nonbrokered_sum=sum(FinalAmountUSD,na.rm = TRUE)) 
nonbrokered_monthly_totals

brokered_monthly_totals <- usefulvar_rawagents %>% filter(ClosedDateYear==2017) %>% filter(Agents!="Non-brokered") %>% group_by(ClosedDateMonth) %>% summarise(brokered_sum=sum(FinalAmountUSD,na.rm = TRUE)) 
brokered_monthly_totals

```





Make data frame to plot brokered and non-brokered. 

First, create new variable "Type" with designation "Non-Brokered" and "Brokered"


```{r}

Type1=rep("Non-Brokered",12)
Type2=rep("Brokered",12)
Type=c(Type1,Type2)
Type

```



Next, revise Brokered variables so there are match 12 values. Same with Non-Brokered. 

```{r}

#NA_twelve_times<- c("NA","NA","NA","NA","NA","NA","NA","NA","NA","NA","NA","NA")


#Brokered_Match_Variables <- c(NA_twelve_times,brokered_monthly_totals$brokered_sum)

#Brokered_Match_Variables

Brokered_Non_Brokered_Together <-append(brokered_monthly_totals$brokered_sum,nonbrokered_monthly_totals$nonbrokered_sum)

Brokered_Non_Brokered_Together

#Non_Brokered_Match_Variables <- c(nonbrokered_monthly_totals$nonbrokered_sum, NA_twelve_times)

#Non_Brokered_Match_Variables

#list_b_nb<-list(c(brokered_monthly_totals$ClosedDateMonth,Brokered_Match_Variables,Non_Brokered_Match_Variables,Type))

#list_b_nb




x <-c("Month","Value","Type")
x

brokered_nonbrokered_comparison <-data.frame(brokered_monthly_totals$ClosedDateMonth,Brokered_Non_Brokered_Together,Type)

brokered_nonbrokered_comparison <-setNames(brokered_nonbrokered_comparison,x)

brokered_nonbrokered_comparison
```




Plot brokered and non-brokered

```{r}


ggplot(data=brokered_nonbrokered_comparison, mapping=aes(x=Month, y=Value, fill=Type))+
  geom_bar(stat="identity") +
  #geom_label(aes(y=Brokered_Non_Brokered_Together), stat="identity") +
  #coord_flip() +
  theme_minimal()


```





Plot non-brokered

```{r}
ggplot(data=nonbrokered_monthly_totals, mapping=aes(x=ClosedDateMonth, y=nonbrokered_sum))+
  geom_bar(stat="identity") +
  #geom_text(aes(label=nonbrokered_sum)) +
  #coord_flip() +
  theme_minimal() +
   #scale_y_continuous(labels = comma) +
 ggtitle("Total Non-Brokered Financings in 2017") +
  xlab("")+
  ylab("")

```



Plot brokered 

```{r}

ggplot(data=brokered_monthly_totals, mapping=aes(x=ClosedDateMonth, y=brokered_sum))+
  geom_bar(stat="identity") +
  #geom_text(aes(label=brokered_sum)) +
  theme_minimal() +
  #scale_y_continuous(labels = comma) +
  ggtitle("Total Brokered Financings in 2017") +
  xlab("")+
  ylab("")



```












////////////////


The Agents variable has multiple observations. Split and give each its own line.This command is in the shop while I check how it is dividing lines.


```{r}

#rawagents_split <-separate_rows(rawagents,Agents,sep="\\|")
#rawagents_split
```


